Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-15 article.tex
Moved @Giappo's feedback about the workflow figure to https://github.com/richelbilderbeek/pirouette_article/issues/26

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a phylogeny (1a) simulated by generative prior 
$\mathit{P}$.
    The phylogeny is converted to an alignment (2a) using alignment model 
$\mathit{A}$. 
    The user supplies one or more experiments.
    For each candidate experiment $\mathit{X}$ 
    (a tuple of inference model $\mathit{I}$ and condition $\mathit{C}$),
    if its condition $\mathit{C}$ is 
    satisfied (which can depend on the alignment), 
    it becomes a selected experiment $\mathit{X'}$, 
    to be used in the next step (3a).
    The inference models of the selected experiment use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, a twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using twinning parameters $T$, where $T$ may depend on
    the experiments \richel{improve}.
    From a twin phylogeny, the same intermediate steps are taken,
    resulting in a twin error distribution (5b)
    \giovanni{Ok, that's my take on this: 1) all the capital letters should go 
in a ball (or a rhombus, as you already did for C) which stands in the middle 
of the arrows (as with C now); 2) The box in the middle should contain all the 
inference models $I_{i}$; 3) We need another C at the intersection of the 
arrows that point to T and A; 4) In between of the arrow 2a->4a there should be 
another rhombus (or circle) with an I (or I' or I*, according on how we want to 
call the selected inference model), which is pointed by the rhombus (of circle) 
containing C; 5) The first arrow should start from a rhombus (or circle) with P 
inside.}
  }
  \label{fig:pipeline}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a phylogeny (1a) simulated by generative prior 
$\mathit{P}$.
    The phylogeny is converted to an alignment (2a) using alignment model 
$\mathit{A}$. 
    The user supplies one or more experiments.
    For each candidate experiment $\mathit{X}$ 
    (a tuple of inference model $\mathit{I}$ and condition $\mathit{C}$),
    if its condition $\mathit{C}$ is 
    satisfied (which can depend on the alignment), 
    it becomes a selected experiment $\mathit{X'}$, 
    to be used in the next step (3a).
    The inference models of the selected experiment use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, a twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using twinning parameters $T$, where $T$ may depend on
    the experiments \richel{improve}.
    From a twin phylogeny, the same intermediate steps are taken,
    resulting in a twin error distribution (5b)
  \label{fig:pipeline}
\end{figure}
